Playing multiple games using deep reinforcement learning, or Spatial Attention network can play (beat) simultaneously multiple games in reinforcement learning

### 2019-09-15 multi_dqn_paper/paper.tex
updated results

\subsection {Network architecture}
Following state of the art \cite{bib:vgg_net} and \cite{bib:resnet_net}, we used only 3x3 kernels with stride 1, instead of 8x8 kernels as in \cite{bib:dqn_atari}.
As activation function the ELU is choosen, with $\alpha = 0.1$. After convolution and pooling layer we used one full connected with 256 units and second
full connected corresponding to actions count in game. For multi\_nets the amount of units on last layer depends on game with maximum possible actions.

@@

{\bf Spatial Attention CNN network architecture}:
The last architecture we tested is Spatial Attention CNN, inspired by \cite{bib:cbam}, multi\_net\_1.
The main idea of attention in CNN is to "amplify" some selected featured and present them to next layer.
Our presented attention module is illustrated on figure \ref{img:spatial_attention_module}.
Input tensor with dimensions $width \times height \times depth$ is processed in convolution block (with kernel size $3 \times 3 \times depth$).
Instead of input features-depth pooling - which is useful in classification attention networks, we are using full features inputs into convolution module (layer).
After convolution the sigmoid non-linear activation is applied on feature maps. Next block is gating unit, which is using point-wise (Hadamard) product.
The last step is addition block, which adds original input and attention features - this can be intepreted as ResNet idea. Full network architectures can be seen in table \ref{tab:networks}.
The formal definition can be written in following term

>>>>

\subsection {Network architecture}
We used three different architecturec for our experiments : basic CNN, DenseNet and Spatial Attention CNN.
Following state of the art \cite{bib:vgg_net} and \cite{bib:resnet_net}, we used only 3x3 kernels with stride 1, instead of 8x8 kernels as in \cite{bib:dqn_atari}.
As activation function the ELU is choosen, with $\alpha = 0.1$. After convolution and pooling layers we used one full connected with 256 units and second
full connected corresponding to actions count in game. For multi\_nets the amount of units on last layer depends on game with maximum possible actions.
All network architectures can be seen in table \ref{tab:networks}.

@@

{\bf Spatial Attention CNN network architecture}:
The last architecture we tested is Spatial Attention CNN, inspired by \cite{bib:cbam}, multi\_net\_2.
The main idea of attention in CNN is to "amplify" some selected featured and present them to next layer.
Our presented attention module is illustrated on figure \ref{img:spatial_attention_module}.
Input tensor with dimensions $width \times height \times depth$ is processed in convolution block (with kernel size $3 \times 3 \times depth$).
Instead of input features-depth pooling - which is useful in classification attention networks, we are using full features inputs into convolution module (layer).
After convolution the sigmoid non-linear activation is applied on feature maps. Next block is gating unit, which is using point-wise (Hadamard) product.
The last step is addition block, which adds original input and attention features - this can be intepreted as ResNet idea.
The formal definition can be written in following term
